### 2016-06-19 finalText/stateArt.tex
Proposed Solution chapter almost done

Furthermore, a 2013 article by Tavear et al.~\cite{Tavear13} proposes, for the first time, using SPSA to train LSTM Neurons, although the article focuses on proving the suitability of SPSA to LSTM, and no factual hardware implementation is done or proposed. The authors simply demonstrate the suitability using conceptual arguments and by building a software model of an SPSA-trained LSTM network, and by comparing both the performance and computing speed of their model with the results achieved by Hochreiter et al. in~\cite{Hochreiter07}. Since the forward phase in both regular LSTM and SPSA-trained LSTM is the same, the computation time suffers no performance penalty whatsoever and the learning ability is preserved to a high degree, showing that SPSA is a valid alternative do BPTT and other similar and more common training schemes.

\section{Final Overview}\label{sec:overview}
As we could attest from this small literature survey, although there is already an hardware implementation os LSTM, there is still a good deal of room for improvement by adding on chip-learning to the system, and also to restrict it to a smaller use of the FPGA resources, allowing it to accomodate a more complex network. Furthermore,~\cite{Tavear13} shows that, at least for that particular case, the LSTM network doesn't suffer a great performance impact from using SPSA training, as opposed to the more common BPTT, and~\cite{Maeda05} showed that an SPSA hardware implementation is feasible. These three conclusions combined indicate that the idea of a hardware LSTM network with on-chip learning using SPSA is possible.

Besides the proposed hardware implementation, it would be advantageous to perform \emph{benchmarks} to see how well it compares with software solutions, and Section~\ref{sec:sa_apps} suggests a handful of examples to test my final solution.

>>>>

Furthermore, a 2013 article by Tavear et al.~\cite{Tavear13} proposes, for the first time, using SPSA to train LSTM Neurons, although the article focuses on proving the suitability of SPSA to LSTM, and no actual hardware implementation is done or proposed. The authors simply demonstrate the suitability using conceptual arguments and by building a software model of an SPSA-trained LSTM network, and by comparing both the performance and computing speed of their model with the results achieved by Hochreiter et al. in~\cite{Hochreiter07}. Since the forward phase in both regular LSTM and SPSA-trained LSTM is the same, the computation time suffers no performance penalty whatsoever and the learning ability is preserved to a high degree, showing that SPSA is a valid alternative do BPTT and other similar and more common training schemes.

\section{Final Overview}\label{sec:overview}
As we could attest from this small literature survey, although there is already an hardware implementation of LSTM, there is still a good deal of room for improvement by adding on chip-learning to the system, and also to restrict it to a smaller use of the FPGA resources, allowing it to accomodate a more complex network. Furthermore,~\cite{Tavear13} shows that, at least for that particular case, the LSTM network doesn't suffer a great performance impact from using SPSA training, as opposed to the more common BPTT, and~\cite{Maeda05} showed that an SPSA hardware implementation is feasible. These three conclusions combined indicate that the idea of a hardware LSTM network with on-chip learning using SPSA is viable.

Besides the proposed hardware implementation, it would be advantageous to perform \emph{benchmarking} to see how well it compares with software solutions, and Section~\ref{sec:sa_apps} suggests a handful of examples to test my final solution.
